Twisted 11-dimensional supergravity, I

### 2021-10-06 nonmin.tex

>>>>

\parsec[sec:indexcheck]

As a first consistency check, we can compare deformation invariants attached to the holomorphic twist and the $G2\times SU(2)$ twist. We will find that the local character of the latter agrees with a specialization of the local character computed in proposition \ref{prop:locchar}

\begin{prop}
The  local character of the $G2\times SU(2)$ twist of 11d supergravity on flat space is given by
\[
\chi_{SU(3)\times SU(2)}(\Obs_0^{\cE_{G2\times SU(2)}}) = \prod _{(n_1,n_2)\in \Z^2_{\geq 0}} \frac{1}{1-q^{-n_1+n_2}}.
\] 
This agrees with the specializaiton of the local character computed in proposition \ref{prop:locchar} at $y=1$.
\end{prop}
\begin{proof}
The space of solutions to linearized equations of motion is parametrized by a holomorphic function $A$ on $\C^2_{w_j}$. The corresponding linear local operators are labeled by $(n_1,n_2)\in \Z^2_{\geq 0}$  and are given by 
\[
A_{(n_1,n_2)} : A \mapsto \partial_{w_1}^{n_1}\partial_{w_2}^{n_2} A (0).
\]

The character of the linear span of these is given by the geometric series
\[
\sum _{(n_1,n_2)\in \Z^2_{\geq 0}} q^{-n_1+n_2}
\] 
with plethystic exponential given by 
\[
\prod _{(n_1,n_2)\in \Z^2_{\geq 0}} \frac{1}{1-q^{-n_1+n_2}}.
\]

For the last part, it suffices to show that the characters of linear local operators agree upon evaluating $y=1$. Summing the geometric series giving the character of linear local operators in the holomorphic twist yields the rational function \[\frac{\left (\begin{aligned}t_1y^{-1} + t_1^{-1}t_2y^{-1} + t_2^{-1}y^{-1} + q^{-1}y^{\frac 3 2} + qy^{\frac 3 2} \\  - (t_1^{-1}y + t_1t_2^{-1}y + t_2y &+ q^{-1}y^{-\frac 3 2} + qy^{-\frac 3 2})\end{aligned}\right)}{(1-t_1^{-1}y)(1-t_1t_2^{-1}y)(1-t_2y)(1-q^{-1}y^{-3/2})(1-qy^{-3/2})}.\] Specializing $y=1$, the numerator cancels with the factors in the denominator involving the $t_i$. The result is \[\frac{1}{(1-q^{-1})(1-q)}\] which is exactly the sum of the geometric series we found

\end{proof}
